A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-11-09 response.tex

\textit{\textbf{R2:} Inspired by the last paragraph of Section 4.1, can authors discuss which of the following is more important for Rust in the next paper version: fixing bugs and fixing compilation errors?}

\vspace*{1em} \noindent \textbf{Response:} Added more discussion regarding this to the last paragraph of Section 4.1. We discuss that we consider bugs as potentially more critical, because an unresolved bug can remain dormant within the system and unintentionally get deployed, whereas a program with compilation errors cannot be shipped by developers.

\vspace*{1em} \noindent \textit{\textbf{R2:} Please discuss why identified patches are all small in the next paper version. Basically, please add the last paragraph of Section 2.2.4 of the rebuttal to the next paper version.}

\vspace*{1em} \noindent \textbf{Response:} Added the mentioned paragraph to the Discussion seciton of the manuscript.

@@

\subsection{Paraphrasing and providing clearer explanation}

\textit{\textbf{R2:} In Section 2.3.2, the authors use sentences from an existing paper directly (although quotes are added). I don't think this is a good way to write an academic paper. Please paraphrase these sentences.}

\vspace*{1em} \noindent \textbf{Response:} Paraphrased the three definitions that were directly quoted.

@@

\vspace*{1em} \noindent \textit{\textbf{R2: } I still do not understand Figure 1. I suggest the authors label ASTDiff nodes with code to ease the explanation.}

\vspace*{1em} \noindent \textbf{Response:} Labeled ASTDiff nodes with code. \todo{Should we add more explanation?}

### 2023-11-09 discussion.tex
reviewer 2 finished for now

>>>>

While we introduce patterns that reflect changes at different locations in the code, such as \textit{BC.ref.add}, which by borrowing a variable instead of taking ownership enables users to use the variable in subsequent locations, we acknowledge that it is possible that a large patch may be harder to cluster, because it has to look like other patches. Additionally, we believe that any clustering-based approach is likely going to have large diffs be further apart for the same reason that ours does: there is just more going on. Nevertheless, there is nothing inherently penalizing a larger diff. Also, we point out that the related work by~\cite{pan2009toward} specifically excludes diffs with seven statements or more, while we allow them.
